Generating the Blueprints of the Java Ecosystem

### 2015-03-30 msr2015-camera-ready.tex
working on the tables

\begin{table}[!t]
\centering
\caption{The selected Maven projects' size metrics.}
\label{tbl:oss-size-metrics}
\begin{tabular}{l r}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 11,365\\
File Count & 449,213\\
Package Count & 59,436\\
Lines of Code & 74,565,772\\
Source Lines of Code & 40,921,287\\
Comment Lines of Code & 25,268,959\\
Number of Classes & 370,518\\
Number of Interfaces & 66,352\\
Number of Enumerations & 9,879\\
Measurement Count & 32,844,836\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\centering
\caption{List of selected {\sc dsl} application libraries.}
\label{tbl:dsl-list}
\begin{tabular}{l l}
 \hline
\textbf{DSL} & \textbf{Java Package}\\
\hline
Regular Expressions & \verb|java.util.regex|\\
XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
SQL & \verb|java.sql| and \verb|javax.sql|\\
XPath & \verb|java.xml.xpath|\\
XSLT & \verb|javax.xml.transform|\\
RTF & \verb|javax.swing.text.rtf|\\
HTML & \verb|javax.swing.text.html|\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\centering
\caption{Class Design Metrics.}
\label{tbl:class-selected-metrics}
\begin{tabular}{l l}
\hline
Depth Of Inheritance Tree & \textit{ckjm}\\
Coupling Between Objects & \textit{ckjm}\\
Weighted Methods Per Class & \textit{ckjm}\\
Response For Class & \textit{ckjm}\\
Lack Of Cohesion In Methods & \textit{ckjm}\\
Number Of Children & \textit{ckjm}\\
Attribute Hiding Factor & \textit{clmt}\\
Coupling Between Methods & \textit{ckjm}\\
Average Method Complexity & \textit{ckjm}\\
Cohesion Among Methods of Class & \textit{ckjm}\\
Data Access Metric & \textit{ckjm, clmt}\\
Inheritance Coupling & \textit{ckjm}\\
Lack Of Cohesion In Methods3 & \textit{ckjm}\\
Measure Of Aggregation & \textit{ckjm}\\
Measure Of Functional Abstraction & \textit{ckjm}\\
Number of Attributes & \textit{clmt}\\
Method Hiding Factor & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{Method Design Metrics.}
\label{tbl:method-selected-metrics}
\begin{tabular}{l l}
\hline
Number of Method Parameters & \textit{clmt}\\
Number of Methods & \textit{clmt, ckjm}\\
McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{Package Design Metrics.}
\label{tbl:package-selected-metrics}
\begin{tabular}{l l}
\hline
Number of Concrete Classes & \textit{jdep}\\
Afferent Couplings & \textit{jdep, ckjm}\\
Efferent Couplings & \textit{jdep, ckjm}\\
Instability & \textit{jdep}\\
Abstractness & \textit{jdep}\\
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{Program Size Metrics.}
\label{tbl:size-selected-metrics}
\begin{tabular}{l l}
 \hline
Number of Classes & \textit{clmt, ckjm, jdep}\\
Number of Enumerations & \textit{clmt, ckjm}\\
Number of Interfaces & \textit{clmt, ckjm}\\
Module Count & \textit{clmt, ckjm}\\
Comments Lines Of Code & \textit{clmt}\\
Lines Of Code & \textit{clmt, ckjm}\\
Source Lines Of Code & \textit{clmt}\\
Function Oriented Code & \textit{clmt}\\
DSL Usage Count & \textit{clmt}\\
RTF Usage Count & \textit{clmt}\\
Regex Usage Count & \textit{clmt}\\
HTML Usage Count & \textit{clmt}\\
XPath Usage Count & \textit{clmt}\\
XSLT Usage Count & \textit{clmt}\\
XML Usage Count & \textit{clmt}\\
SQL Usage Count & \textit{clmt}\\
File Count & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[!t]
\caption{The selected Maven projects' size metrics.}
\label{tbl:oss-size-metrics}
\centering
\begin{tabular}{|l||r|}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 11,365\\
\hline
File Count & 449,213\\
\hline
Package Count & 59,436\\
\hline
Lines of Code & 74,565,772\\
\hline
Source Lines of Code & 40,921,287\\
\hline
Comment Lines of Code & 25,268,959\\
\hline
Number of Classes & 370,518\\
\hline
Number of Interfaces & 66,352\\
\hline
Number of Enumerations & 9,879\\
\hline
Measurement Count & 32,844,836\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\centering
\caption{List of selected {\sc dsl} application libraries.}
\label{tbl:dsl-list}
\begin{tabular}{|l||l|}
 \hline
\textbf{DSL} & \textbf{Java Package}\\
\hline
Regular Expressions & \verb|java.util.regex|\\
\hline
XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
\hline
SQL & \verb|java.sql| and \verb|javax.sql|\\
\hline
XPath & \verb|java.xml.xpath|\\
\hline
XSLT & \verb|javax.xml.transform|\\
\hline
RTF & \verb|javax.swing.text.rtf|\\
\hline
HTML & \verb|javax.swing.text.html|\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Class Design Metrics.}
\label{tbl:class-selected-metrics}
\centering
\begin{tabular}{|l||l|}
\hline
Depth Of Inheritance Tree & \textit{ckjm}\\
\hline
Coupling Between Objects & \textit{ckjm}\\
\hline
Weighted Methods Per Class & \textit{ckjm}\\
\hline
Response For Class & \textit{ckjm}\\
\hline
Lack Of Cohesion In Methods & \textit{ckjm}\\
\hline
Number Of Children & \textit{ckjm}\\
\hline
Attribute Hiding Factor & \textit{clmt}\\
\hline
Coupling Between Methods & \textit{ckjm}\\
\hline
Average Method Complexity & \textit{ckjm}\\
\hline
Cohesion Among Methods of Class & \textit{ckjm}\\
\hline
Data Access Metric & \textit{ckjm, clmt}\\
\hline
Inheritance Coupling & \textit{ckjm}\\
\hline
Lack Of Cohesion In Methods3 & \textit{ckjm}\\
\hline
Measure Of Aggregation & \textit{ckjm}\\
\hline
Measure Of Functional Abstraction & \textit{ckjm}\\
\hline
Number of Attributes & \textit{clmt}\\
\hline
Method Hiding Factor & \textit{clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\caption{Method Design Metrics.}
\label{tbl:method-selected-metrics}
\centering
\begin{tabular}{|l||l|}
\hline
Number of Method Parameters & \textit{clmt}\\
\hline
Number of Methods & \textit{clmt, ckjm}\\
\hline
McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\caption{Package Design Metrics.}
\label{tbl:package-selected-metrics}
\centering
\begin{tabular}{|l||l|}
\hline
Number of Concrete Classes & \textit{jdep}\\
\hline
Afferent Couplings & \textit{jdep, ckjm}\\
\hline
Efferent Couplings & \textit{jdep, ckjm}\\
\hline
Instability & \textit{jdep}\\
\hline
Abstractness & \textit{jdep}\\
\hline
Distance Main Sequence & \textit{jdep}\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\caption{Program Size Metrics.}
\label{tbl:size-selected-metrics}
\centering
\begin{tabular}{|l||l|}
 \hline
Number of Classes & \textit{clmt, ckjm, jdep}\\
\hline
Number of Enumerations & \textit{clmt, ckjm}\\
\hline
Number of Interfaces & \textit{clmt, ckjm}\\
\hline
Module Count & \textit{clmt, ckjm}\\
\hline
Comments Lines Of Code & \textit{clmt}\\
\hline
Lines Of Code & \textit{clmt, ckjm}\\
\hline
Source Lines Of Code & \textit{clmt}\\
\hline
Function Oriented Code & \textit{clmt}\\
\hline
DSL Usage Count & \textit{clmt}\\
\hline
RTF Usage Count & \textit{clmt}\\
\hline
Regex Usage Count & \textit{clmt}\\
\hline
HTML Usage Count & \textit{clmt}\\
\hline
XPath Usage Count & \textit{clmt}\\
\hline
XSLT Usage Count & \textit{clmt}\\
\hline
XML Usage Count & \textit{clmt}\\
\hline
SQL Usage Count & \textit{clmt}\\
\hline
File Count & \textit{clmt}\\
\hline
\end{tabular}
\end{table}
